Disagreement Regarding 2016 Presidential Election in the United States^[Code and data are available at: https://github.com/SANGWOONG-LEE/Thailand_Healthcare]

### 2022-04-02 outputs/paper/paper.Rmd

urban_rural <- pivot_longer(data[1:2, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
region <- pivot_longer(data[3:7, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
education <- pivot_longer(data[8:11, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
religion <- pivot_longer(data[12:13, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
total <- pivot_longer(data[14, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
population <- data.frame(Variable = data$Variable, Population = data$Number_of_Children)

>>>>

urban_rural <- pivot_longer(data[1:2, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
region <- pivot_longer(data[3:7, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
education <- pivot_longer(data[8:11, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
religion <- pivot_longer(data[12:13, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
total <- pivot_longer(data[14, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
population <- data.frame(Variable = data$Variable, 
                         Population = data$Number_of_Children) %>% head(-1)
population$Variable <- factor(population$Variable,
                              levels = population$Variable) %>% fct_rev()
```

```{r}
